Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-07 Paper/paper.tex
Manual CI, Template Files

\subsection{CI By Hand}
Most of what these CI frameworks accomplish can be done by hand.
\todo{Finish this section}

% Strengths
- Similar to Jenkins

% Weaknesses
- Setup by hand
- Uses your machine

@@

\normalsize
\FloatBarrier
\begin{table}[ht]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & GitHub & Other Repos & Multi-Language & Active Development** & GUI Configuration \\ \hline
Jenkins   & X*     & X*          & X*             & X*                  & X                 \\ \hline
Travis    & X      &             & X              &                     &                   \\ \hline
Semaphore & X      &             & X              & X                   & X                 \\ \hline
MagnumCI  & X      & X           & X              & X                   & X                 \\ \hline
Drone.io  & X      & X           & X              & X                   & X                 \\ \hline
Manual    &        & X           & X              & X                   &                   \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Continuous Integration Frameworks}
\end{table}
\FloatBarrier
\footnotesize

@@

@@

@@

>>>>

\subsection{Manual Continuous Integration}
Most of what these CI frameworks accomplish can be done by hand with enough script writing. Continuous Integration tools are notified of updates by scripts that run after a commit is pushed. With the Continuous Integration scripts above, the post commit scripts are written without the knowledge of the developer. There is, however, no reason that a developer cannot hook into those scripts themselves.

Manual CI is incredibly similar to Jenkins in that its only limitations are the libraries and hardware that it's run on.

There are a few differences between Jenkins and Manual CI, the biggest being that Jenkins has a GUI. This GUI is used to configure the project while manual CI requires script and text editing.

Another big difference between Manual CI and all of the other CI frameworks is that the non-manual frameworks store information regarding the status of builds, the success and failure of builds, which files changed in each commit, and a lot of other information that can be quickly viewed. It is possible to store this information manually, but it would require considerable effort to make it as easy to use as the other CI frameworks.

Finally, manual CI uses a developer's system, rendering it unusable to the developer, particularly during the UI testing phase. The developer must accept a productivity hit every time they commit to their repository.

@@

\normalsize
\FloatBarrier
\begin{table}[ht]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & GitHub & Other Repos & Multi-Language & Active Development** & GUI Configuration \\ \hline
Jenkins   & X*     & X*          & X*             & X                    & X                 \\ \hline
Travis    & X      &             & X              &                      &                   \\ \hline
Semaphore & X      &             & X              & X                    & X                 \\ \hline
MagnumCI  & X      & X           & X              & X                    & X                 \\ \hline
Drone.io  & X      & X           & X              & X                    & X                 \\ \hline
Manual    &        & X           & X              & X                    &                   \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Continuous Integration Frameworks}
\end{table}
\FloatBarrier
\footnotesize

@@

MagnumCI was chosen over manual CI for much the same reasons as it was chosen over Jenkins. Manual CI requires an extraordinary effort on the part of the developer if they wish to have all of the features and history of the other CI frameworks.

@@

Following the setup instructions will be a more thorough Gruntfile that can serve as a template and starting point for developers. The Gruntfile will have tasks that will run the Unit Testing and the UI Testing.

@@

\subsection{Template Files}
In order to get developers up and running as quickly as possible, we've included a couple template files below that will get them started out.

The first file is the \lstinline{package.json} file that includes the dependencies for the unit testing, UI testing, and grunt portions of the workflow:
\begin{lstlisting}
{
  "name": "MODULE_NAME", // Edit Me
  "version": "SOME_NUMBER", // Edit Me
  "dependencies": {
    "grunt": "latest",
    "grunt-contrib-watch": "latest",
    "grunt-shell": "latest",
    "grunt-mocha-test": "^0.10.2"
    "mocha": "^1.18.2",
    "istanbul": "^0.2.7",
    "nightwatch": "^0.4.9",
    "chai": "^1.9.1"
  }
}
\end{lstlisting}

Next is an example \lstinline{gruntfile.js} that will get grunt up and running quickly:
\begin{lstlisting}
module.exports = function(grunt)
{
    // Configure Grunt
    grunt.initConfig({
        pkg: grunt.file.readJSON('package.json'),
        shell: {
            npm: {
                command: 'npm update',
                options: {
                    stdout: true
                }
            },
            istanbul: {
                command: 'istanbul cover _mocha --  PATH_TO_TESTS -R spec', // Edit Me
                options: {
                    stdout: true
                }
            }
        },
        watch: {
            test: {
                options: {
                    spawn: false // So watch actually works!
                },
                files: ['**/*.js'],
                tasks: ['mochaTest']
            },
            coverage: {
              options: {
                    spawn: false // So watch actually works!
                },
                files: ['**/*.js'],
                tasks: ['shell:istanbul']
            }
        },
        mochaTest: {
            test: {
                options: {
                    reporter: 'spec',
                    clearRequireCache: true
                },
                src: ['ABSOLUTE_PATH_TO_TESTS'] // Edit Me
            }
        }
    });

    var defaultTestSrc = grunt.config('mochaTest.test.src');
    grunt.event.on('watch', function(action, filepath) {
        grunt.config('mochaTest.test.src', defaultTestSrc);
        if (filepath.match('RELATIVE_PATH_TO_TESTS')) { // Edit Me
          grunt.config('mochaTest.test.src', filepath);
        }
    });

    // Load libs
    grunt.loadNpmTasks('grunt-contrib-watch');
    grunt.loadNpmTasks('grunt-mocha-test');
    grunt.loadNpmTasks('grunt-shell');

    // Register the default tasks
    grunt.registerTask('default', ['mochaTest']);

    // Register update task
    grunt.registerTask('update', ['shell:npm']);

    // Register the mocha test task
    grunt.registerTask('test', ['mochaTest', 'watch:test']);

    // Register the code coverage task
    grunt.registerTask('test_with_coverage', ['shell:istanbul', 'watch:coverage']);
};
\end{lstlisting}
